% ============================================================================
% REFERENCES
% ============================================================================
{\small
\bibliographystyle{IEEEtran}
\begin{thebibliography}{99}

    \bibitem{mildenhall2020nerf}
    B.~Mildenhall, P.~P.~Srinivasan, M.~Tancik, J.~T.~Barron, R.~Ramamoorthi, and R.~Ng,
    ``NeRF: Representing scenes as neural radiance fields for view synthesis,''
    in \emph{ECCV}, 2020.

    \bibitem{kerbl20233dgs}
    B.~Kerbl, G.~Kopanas, T.~Leimk{\"u}hler, and G.~Drettakis,
    ``3D Gaussian Splatting for real-time radiance field rendering,''
    \emph{ACM Trans. Graphics}, vol.~42, no.~4, 2023.

    \bibitem{huang20242dgs}
    B.~Huang, Z.~Yu, A.~Chen, A.~Geiger, and S.~Gao,
    ``2D Gaussian Splatting for geometrically accurate radiance fields,''
    in \emph{SIGGRAPH}, 2024.

    \bibitem{joaxkal2024lumigauss}
    J.~Kaleta,
    ``LumiGauss: Relightable Gaussian Splatting in the Wild,''
    in \emph{WACV}, 2025.

    \bibitem{rudnev2022nerfOSR}
    V.~Rudnev, M.~Elgharib, W.~Smith, L.~Liu, V.~Golyanik, and C.~Theobalt,
    ``NeRF for outdoor scene relighting,''
    in \emph{ECCV}, 2022.

    \bibitem{martinbrualla2021nerfw}
    R.~Martin-Brualla, N.~Radwan, M.~S.~M.~Sajjadi, J.~T.~Barron, A.~Dosovitskiy, and D.~Duckworth,
    ``NeRF in the Wild: Neural radiance fields for unconstrained photo collections,''
    in \emph{CVPR}, 2021.

    \bibitem{williams1978casting}
    L.~Williams,
    ``Casting curved shadows on curved surfaces,''
    \emph{Computer Graphics (SIGGRAPH)}, vol.~12, no.~3, pp.~270--274, 1978.

    \bibitem{preetham1999practical}
    A.~J.~Preetham, P.~Shirley, and B.~Smits,
    ``A practical analytic model for daylight,''
    in \emph{SIGGRAPH}, 1999.

    \bibitem{nishita1993display}
    T.~Nishita, T.~Sirai, K.~Tadamura, and E.~Nakamae,
    ``Display of the earth taking into account atmospheric scattering,''
    in \emph{SIGGRAPH}, 1993.

    \bibitem{lalonde2012estimating}
    J.-F.~Lalonde, A.~A.~Efros, and S.~G.~Narasimhan,
    ``Estimating the natural illumination conditions from a single outdoor image,''
    \emph{IJCV}, vol.~98, no.~2, pp.~123--145, 2012.

    \bibitem{hold-geoffroy2019deep}
    Y.~Hold-Geoffroy, A.~Athawale, and J.-F.~Lalonde,
    ``Deep sky modeling for single image outdoor lighting estimation,''
    in \emph{CVPR}, 2019.

    \bibitem{meeus1991astronomical}
    J.~Meeus,
    \emph{Astronomical Algorithms}.
    Willmann-Bell, 1991.

    \bibitem{yu2021outdoor}
    \todo{Yu et al. -- outdoor relighting reference.}

    \bibitem{philip2019multiview}
    \todo{Philip et al. -- multi-view relighting reference.}

    \bibitem{jin2023tensoir}
    \todo{SR-TensoRF reference.}

    \bibitem{fegr2024}
    \todo{FEGR reference.}

    \bibitem{solnerf2024}
    \todo{SOL-NeRF reference.}

    \bibitem{neusky2024}
    \todo{NeuSky reference.}

\end{thebibliography}
}